\documentclass[dvipsnames]{simplenote}    % Specifies the document style.
% \documentclass[dvipsnames]{cernatsnote}    % Specifies the document style.
\usepackage{amssymb}
\usepackage[T1]{fontenc}  % allows for \textsc and \textbf in one 
\usepackage{xstring}  % string manipulation
\usepackage[normalem]{ulem} % underlines
\usepackage{cite}
\usepackage{xfrac}

\listfiles  % writes current versions into log
\input{userdef.tex}
% Meta-Data %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

% \documentlabel{CERN-ACC-NOTE-2022-???}
\documentversion{Version 1.0}
\date{05.07.2022}
\title{A flexible nonlinear Resonance Driving Term based Correction Algorithm with feed-down}
\author{J. Dilly, R. Tom\'as}

% logbook: 
% Document Begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\keywords{nonlinear correction, insertion region, feed-down, LHC, HL-LHC, HiLumi}

\begin{document}
\graphicspath{
    {./images/}
    %{./images/}
}
\maketitle 

\begin{abstract}
The optics in the insertion regions around the interaction points of the LHC, and its upgrade project the High Luminosity LHC, 
are very sensitive to local magnetic errors due to the extremely high beta-functions present.
Local corrections need to take both beams into account, due to the common aperture of the magnets in these regions.
In collision optics, the non-zero closed orbit around the interaction point leads to a ``feed-down'' of high-order errors to lower orders, 
causing additional effects detrimental to beam lifetime. 
An extension to the proven method~\cite{BruningDynamicApertureStudies2004} for correcting these errors by locally suppressing resonance driving terms has been undertaken, 
not only taking this feed-down into account, but also adding the possibility of utilizing it such that the powering of higher-order correctors will compensate 
for lower order errors.
The existing correction scheme has also operated on the assumption of symmetric beta-functions of the optics in the two rings.
As this assumption can fail for a multitude of reasons, such as inherently asymmetric optics, 
an extension of this correction scheme has been developed removing the need for symmetry by operating on the two separate optics of the beams at the same time.
In contrast to earlier implementations, the target resonance driving terms to be corrected can also be flexibly changed. 
The mathematical background as well as the implementation of this new extension are presented in this note.
\end{abstract}


\tableofcontents
\newpage

% Motivation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{01_motivation}


% Mathematical Description %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\FloatBarrier
\input{02_background}

% Implementation Details %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\FloatBarrier
\input{03_implementation}

% Applications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\FloatBarrier
\input{04_applications}

% Conclusion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\FloatBarrier
\input{05_conclusion}

% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\FloatBarrier

\bibliographystyle{siamurl}
\bibliography{library_jdilly.bib}
\clearpage

% Appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \FloatBarrier
% \input{appendix}

\end{document}
